---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/vincenzocoia/powers)

__Note__: This R package is not mean to be "serious". It's just for teaching purposes. 

# powers

This is an R package that gives `sqrt()` friends by providing other power functions.

# Contribution

For homework 7, I have developed a function `BoxCoxTrans()` that transforms data using a Box-Cox Transformation. 
The function exists [here](https://github.com/STAT545-UBC-students/hw07-j-schaub/blob/master/R/CoxBoxTransform.R). 
Please see the [vignette](https://github.com/STAT545-UBC-students/hw07-j-schaub/blob/master/vignettes/using_powers.Rmd) for a usage example and the [document](https://github.com/STAT545-UBC-students/hw07-j-schaub/blob/master/man/BoxCoxTrans.Rd) for a description of the function.

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("j-schaub/powers")
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example}
powers::square(2)

```

## For Developers

(Again, I don't actually intend for anyone to develop this silly package, but if I did, here's what I'd write.)

Use the internal `pow` function as the machinery for the front-end functions such as `square`, `cube`, and `reciprocal`. 
